%-------------------------
% Resume in Latex
% Author : Kyle Capehart
% License : MIT
% Inspired by: https://github.com/arasgungore/arasgungore-CV
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{multicol}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{fontawesome}
\usepackage[dvipsnames]{xcolor}
\input{glyphtounicode}


%---------- FONT OPTIONS ----------
% sans-serif
\usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}
% \usepackage[default]{lato}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bf\color{NavyBlue}
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[2]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeOrganizationHeading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
      \textit{\small#3}
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}


%---------- HEADING ----------

\begin{center}
    \textbf{\Huge \color{NavyBlue} Ishara Dilshan $|$ Software Engineer} \\ \vspace{10pt}
    \faPhoneSquare \hspace{.5pt} {+94717809280}
    $|$
    \faEnvelope \hspace{.5pt} \href{mailto:isharadilshandev@gmail.com}{isharadilshandev@gmail.com}
    $|$
    \faLinkedinSquare \hspace{.5pt} \href{https://www.linkedin.com/in/isharadilshan/}{in/isharadilshan}
    $|$
    \faGithub \hspace{.5pt} \href{https://github.com/isharadilshan}{isharadilshan}
    $|$
    \faStackOverflow \hspace{.5pt} \href{https://stackoverflow.com/users/7469665/ishara-dilshan}{ishara-dilshan}
\end{center}

\cfoot{\scriptsize{\color{gray}Ishara Dilshan $|$ CV}}

\vspace{8pt}
\begin{center}
  \textit{Experienced Frontend developer with a passion in mobile app development and 4.5+ years in the industry. Excited to join a talented team and build world-class apps.}
\end{center}
\vspace{8pt}

%----------- EXPERIENCE -----------

\section{Experience}
  \vspace{16pt}
  \resumeSubHeadingListStart
  
    \resumeSubheading
      {Sr. Software Engineer @ Swivel Group  $|$  \footnotesize{\emph{\href{https://swivelgroup.com.au}{swivelgroup.com.au}}}}{\color{NavyBlue}Aug 2022 \textbf{--} Present}
      \vspace{2pt}
        \resumeItemListStart
            \resumeItem{Developed and managed white label applications using React Native.}\href{https://apps.apple.com/lk/developer/smata-technologies/id1573302370}{\color{NavyBlue}https://apps.apple.com/lk/developer/smata-technologies/id1573302370}
            \resumeItem{Managed deployments on DEV, QA, UAT, PROD environments with fastlane, GitHub Actions, Firebase App Distribution and stores.}
            \resumeItem{Responsible for developing Message [ \textbf{Webhooks} ] and Maps features.}
            \resumeItem{Provided technical leadership by mentoring junior engineers, code reviews and requirement gathering.}
        \resumeItemListEnd
        \vspace{16pt}

    \resumeSubheading
      {Sr. Software Engineer @ Arimac $|$  \footnotesize{\emph{\href{https://arimaclanka.com}{arimaclanka.com}}}}{\color{NavyBlue}July 2021 \textbf{--} Aug 2022}
      \vspace{4pt}
        \resumeItemListStart
            \resumeItem{Actively developed a React Native cross-platform app for DU Mobile, the leading telecom provider in the UAE.}\href{https://play.google.com/store/apps/details?id=duleaf.duapp.splash}{\color{NavyBlue}https://play.google.com/store/apps/details?id=duleaf.duapp.splash}
            \resumeItem{Integrated Firebase services \textbf{Crashlytics}, \textbf{Analytics}, \textbf{Dynamic Links}, and \textbf{Remote Config} into the project for optimal performance and data analysis.}
            \resumeItem{Responsible for the development of  animation feature using \textbf{Lottie} for both iOS and Android platforms.}
            \resumeItem{Contributed to the integration of a static code quality analyzer \textbf{SonarQube}, automating the assessment of code quality for every pull request.}
        \resumeItemListEnd
        \vspace{16pt}

    \resumeSubheading
      {Software Engineer @ ObjectOne pvt Ltd $|$  \footnotesize{\emph{\href{https://www.objectoneworld.com}{objectoneworld.com}}}}{\color{NavyBlue}July 2020 \textbf{--} July 2021}
      \vspace{4pt}
        \resumeItemListStart
            \resumeItem{Actively contributed to the development of a cross-platform self-care application (Ncell-Saathi) for Dialog Axiata in Nepal.}\href{https://play.google.com/store/apps/details?id=com.mventus.ncell.activity}{\color{NavyBlue}https://play.google.com/store/apps/details?id=com.mventus.ncell.activity}
            \resumeItem{Responsible for deploying applications to the Google Play Store using Microsoft AppCenter and to the Apple App Store utilizing Xcode.}
            \resumeItem{Integrated \textbf{CodePush} service for seamless deployment of application updates ( \textbf{OTA} ) directly to end users.}
        \resumeItemListEnd
        \vspace{16pt}

    \resumeSubheading
      {Associate Software Engineer @ Zegates International $|$ \footnotesize{\emph{\href{https://zegates.com/}{zegates.com}}}}{\color{NavyBlue}Feb 2020 \textbf{--} July 2020}
      \vspace{4pt}
        \resumeItemListStart
            \resumeItem{Developed React-Native/Redux code using functional programming best practices and SOLID concepts}
            \resumeItem{Experience with integrating \textbf{REST} APIs and  \textbf{GraphQL}.}
            \resumeItem{Contributed to projects including healthcare, finance, and e-commerce sectors}
        \resumeItemListEnd
        \vspace{16pt}

    \resumeSubheading
      {Trainee Software Engineer @ Infor $|$  \footnotesize{\emph{\href{https://infor.com/}{infor.com}}}}{\color{NavyBlue}Aug 2019 \textbf{--} Feb 2020}
      \vspace{4pt}
        \resumeItemListStart
            \resumeItem{Developed and maintained automated CI/CD pipelines for code analysis and deployment using  \textbf{Jenkins},  \textbf{Sonarqube}, and \textbf{GitLab API}}
            \resumeItem{Contributed to version upgrade of an \textbf{Ionic} project.}
            \resumeItem{Actively contributed to developing \textbf{NPM} library to streamline the internal JavaScript framework by reducing codebase size, minimizing dependencies, and eliminating duplicate code.}
        \resumeItemListEnd
        \vspace{16pt}
    
  \resumeSubHeadingListEnd


%----------- PROJECTS -----------
\vspace{48pt}
\section{Projects}
    \vspace{16pt}
    \resumeSubHeadingListStart
      
      \resumeProjectHeading
        {\textbf{Outopia} $|$ \emph{\href{https://www.outopia.ch}{\color{NavyBlue}outopia.ch}}}{}
          \resumeItemListStart
            \resumeItem{Switzerland based startup travel company website written in \textbf{React}}
            \resumeItem{Implemented Admin panel and added \textbf{tailwindcss} framework and localization support for the main website}
          \resumeItemListEnd
      
      \resumeProjectHeading
        {\textbf{RN npm module} $|$ \emph{\href{https://www.npmjs.com/package/react-native-typewritter}{\color{NavyBlue}react-native-typewritter}}}{}
          \resumeItemListStart
            \resumeItem{A simple component for adding a nice typewriter effect to your react native project.}
          \resumeItemListEnd

      \resumeProjectHeading
        {\textbf{IOT temp sensing and monitor module} $|$ \emph{\href{https://gritires.com}{\color{NavyBlue}grityres.com}}}{}
          \resumeItemListStart
            \resumeItem{Worked on backend written on Laravel to collect data from temp sensing module integrated on Arduino}
            \resumeItem{Implemented admin panel and integrated chart.js to visualize data}
          \resumeItemListEnd

      \resumeProjectHeading
        {\textbf{Resum shortlisting platform}}{}
          \resumeItemListStart
            \resumeItem{Contributed to resum shortlisting platform admin portal web application development in Next.JS}
          \resumeItemListEnd
      
    \resumeSubHeadingListEnd


%----------- EDUCATION & CERTIFICATIONS -----------
\vspace{8pt}
\section{Education \& Certifications}
  \vspace{16pt}
  \resumeSubHeadingListStart

    \resumeSubheading
      {University of Colombo School of Computing}{}
      \resumeSubSubheading{B.Sc in Computer Science}{\color{NavyBlue}Jan 2020}
    \vspace{7pt}

    \resumeSubheading
      {Sri Lanka Vocational Training Center, Dehiwala}{}
      \resumeSubSubheading{Diploma in Networking and Computer Hardware}{\color{NavyBlue}July 2018}

  \resumeSubHeadingListEnd

  %----------- SKILLS -----------
\vspace{1pt}
\section{Skills}
  \begin{multicols}{2}

    \textbf{Frontend:}{ React, Next.JS, React Native, Android } \\ \vspace{3pt}
    \textbf{Backend:}{ Node, Laravel } \\ \vspace{3pt}
    \textbf{DevOps:}{ Github Actions, Jenkins, Fastlane, Appcenter } \\ \vspace{3pt}

    \columnbreak

    \textbf{Databases:}{ MySql, MongoDB, Firebase Firestore } \\ \vspace{3pt}
    \textbf{SDLC:}{ JIRA, Trello } \\ \vspace{3pt}
    \textbf{Testing:}{ Jest, Detox } \\ \vspace{3pt}
      
  \end{multicols}

%----------- REFERENCES -----------
\vspace{1pt}
\section{References}
  \begin{multicols}{2}
    \textbf{Duminda Gunawardana - Manager Software Development}
      \\\textbf{\small{Infor}}
      \\\textit{duminda.gunawardena@infor.com}
      \\\textsc{0114 - 768 300 ext: 2842}

    \columnbreak

    \textbf{Kasun Gunawardena - Senior Lecturer}
      \\\textbf{\small{University of Colombo School of Computing}}
      \\\textit{kgg@ucsc.cmb.ac.lk}
      \\\textsc{0112 - 158 971}
      
  \end{multicols}

\end{document}